\section{Articles de revue}

\cventry{2022}{Homogenized constitutive
  equations for porous single crystals plasticity.}{Cédric Sénac,
  Jean-Michel Scherer, Jérémy Hure, Thomas Helfer et Benoît
  Tanguy}{European Journal of Mechanics / A Solids}{}{}

\cventry{2021}{Large-deformation
  geomechanical problems studied by a shear-transformation-zone model
  using the material point method.}{Wenlong Li, Ning Guo, Z.X. Yang, et
  Thomas Helfer.}{Computers and
  Geotechnics.}{\url{10.1016/j.compgeo.2021.104153}}{}{}

\cventry{2020}{Philippe Garcia, Audrey Miard,
  Thomas Helfer, Jean-Baptiste Parise, Xavière Iltis et Guy Antou}{The
  effect of oxygen partial pressure on dislocation creep in
  polycrystalline uranium dioxide}{Journal of the European Ceramic
  Society.}{\url{10.1016/j.jeurceramsoc.2020.09.005}}{}

\cventry{2020}{The MFrontGenericInterfaceSupport project}{}{Journal of
  Open Source Software}{Thomas Helfer, Jérémy Bleyer, Tero Frondelius,
  Ivan Yashchuk, Thomas Nagel and Dmitri Naumov}{}{}

\cventry{2020}{An efficient and robust staggered algorithm applied to
  the quasi-static description of brittle fracture by a phase-field
  approach}{Ye Lu, Thomas Helfer and Olivier Fandeur}{Computer Methods
  in Applied Mechanics and Engineering}{}{}

\cventry{2019}{Description and thermal simulation of the DIAMINO
  irradiation experiment of transmutation fuel in the OSIRIS
  reactor}{Syriac Bejaoui, Thomas Helfer, Stéphane Bendotti and
  Thierry Lambert}{Progress in Nuclear Energy}{}{}

\cventry{2018}{Crystal viscoplastic modeling of UO2 single
  crystal}{Luc Portelette, Jonathan Amodeo, Ronan Madec, Julian
  Soulacroix, Thomas Helfer and Bruno Michel}{Journal of Nuclear
  Materials}{}{}

\cventry{2018}{Simulation of
  reactivity-initiated accident transients on UO2-M5® fuel rods with
  ALCYONE V1.4 fuel performance code}{ Isabelle Guénot-Delahaie, Jérôme
  Sercombe, Patric Goldbronn, , Eric Federici, Thomas Le Jolu, Aurore
  Parrot, Christine Delafoy, and Christian Bernaudat }{Nuclear
  Engineering and Technology.}{\url{10.1016/j.net.2017.12.006}}{}

\cventry{2017}{Analytical and 3D numerical analysis of the
  thermoviscoelastic behavior of concrete-like materials including
  interfaces}{Benoit Bary, Christophe Bourcier and Thomas
  Helfer}{Advances in Engineering Software}{}{}

\cventry{2016}{3D Continuum Damage Approach for
  Simulation of Crack Initiation and Growth in Ceramic Materials.}{Bruno
  Michel, Thomas Helfer, Isabelle Ramière et Coralie Esnoul.}{Key
  Engineering
  Materials.}{\url{10.4028/www.scientific.net/KEM.713.155}}{}

\cventry{2016}{A new numerical methodology for
  simulation of unstable rupture in fragile materials}{Bruno Michel,
  Thomas Helfer, Isabelle Ramière, and Coralie Esnoul}{Engineering
  Fracture Mechanics}{}{}

\cventry{2016}{2D simulation of hydride blister cracking during a RIA
  transient with the fuel code ALCYONE}{Jérôme Sercombe, Thomas
  Helfer, Eric Federici, David Leboulch, Thomas Le Jolu, Arthur
  Hellouin de Ménibus, and Christian Bernaudat}{EPJ Nuclear Sciences \&
  Technologies, 2 :22, 2016}{}{}

\cventry{2016}{Thermoviscoelastic Analysis of Concrete Creep at
  Mesoscale}{Benoit Bary, Christophe Bourcier, and Thomas Helfer}{Key
  Engineering Materials, 711 :652–658, September 2016}{}{}

\cventry{2015}{Iterative residual-based vector methods to accelerate
  fixed point iterations}{Isabelle Ramière, Thomas Helfer}{Computers
  \& Mathematics with Applications, Volume 70, Issue 9, November 2015,
  Pages 2210-2226}{}{}

\cventry{2015}{Introducing the open-source mfront code generator:
  Application to mechanical behaviours and material knowledge
  management within the PLEIADES fuel element modelling
  platform}{Thomas Helfer,Bruno Michel, Jean-Michel Proix, Maxime
  Salvo, Jérôme Sercombe, Michel Casella}{Computers \& Mathematics
  with Applications, Volume 70, Issue 5, September 2015, Pages
  994-1023}{}{}

\cventry{2015}{Extension of monodimensional fuel performance codes to
  finite strain analysis using a lagrangian logarithmic strain
  framework}{Thomas Helfer}{Nuclear Engineering And Design, Volume 288, July 2015, Pages 75-81}{}{}

\cventry{2015}{Licos, a fuel performance code for
  innovative fuel elements or experimental devices design.}{Thomas
  Helfer, Syriac Bejaoui et Bruno Michel.}{Nuclear Engineering and
  Design}{\url{10.1016/j.nucengdes.2015.07.070}}{}

\cventry{2015}{Current status in PLEIADES fuel performance codes of
  cracks and damage modelling}{Thomas Helfer, Bruno Michel, Jérôme
  Sercombe}{International Conference on Computational Modeling of
  Fracture and Failure of Materials and Structures}{Paris}{}

\cventry{2015}{Experimental characterization and modeling of UO2 grain
  boundary cracking at high temperatures and high strain rates}{Maxime
  Salvo, Jérôme Sercombe, Thomas Helfer, Philippe Sornay, Thierry
  Désoyer}{Journal of Nuclear Materials, Volume 460, May 2015, Pages
  184-199}{}{}

\cventry{2015}{Experimental characterization and modelling of UO2
  behavior at high temperatures and high strain rates}{Maxime Salvo,
  Jérôme Sercombe, Jean-Claude Ménard, Jérôme Julien, Thomas Helfer,
  Thierry Désoyer}{Journal of Nuclear Materials, Volume 456, January
  2015, Pages 54-67}{}{}

\cventry{2013}{Stress concentration during pellet cladding
  interaction: Comparison of closed-form solutions with
  \(2D\left(r,\theta\right)\) finite element simulations}{Jérôme
  Sercombe, Renaud Masson, Thomas Helfer}{Nuclear Engineering and
  Design, Volume 260, July 2013}{}{}

\section{Chapitres de livre}

\cventry{2021}{Two fuel performance codes of the
  PLEIADES platform: ALCYONE and GERMINAL.}{Bruno Michel, Isabelle
  Ramière, I. Vaillard, Clément Introïni, Marc Lainet, Nathalie Chauvin,
  Vincent Marelle, Antoine Bouloré, Thomas Helfer, Renaud Masson, Jérôme
  Sercombe, Jean-Christophe Dumas, Laurence Noirot, Stéphane
  Bernaud.}{Nuclear Power Plant Design and Analysis Codes
  .}{\url{10.1016/B978-0-12-818190-4.00009-7}}{}{}

\section{Participatation à congrès}

\cventry{2023}{Understanding AM 316L steel
  microstructure evolution due to post-process laser scanning: a
  thermo-mechanical modeling and in-situ laser-SEM study.}{Nikhil
  Mohanan, Juan Guillermo Santos Macias, Jérémy Bleyer, Thomas Helfer
  and Manas Upadhyay}{2023 TMS Annual Meeting \& Exhibition}{March
  19–23}{San Diego, California, USA}

\cventry{2022}{Development of a novel damage
  model for concrete accounting for creep, high temperature, and
  constraint effects}{￼Jefri Draup, Alexandre Gangnant, Graham Doughty,
  Jiansong Guo, Thomas Helfer, Giacomo Torelli}{Structural Mechanics in
  Reactor Technology}{July 2022}{Berlin, Germany}

\cventry{2022}{Flexible integration of
  constitutive models into simulators for non- isothermal two-phase flow
  in deformable porous and fractured media}{Thomas Nagel, Thomas
  Helfer, Michael Pitz, Dmitri Naumov, Norbert Grunwald, Sonja Kaiser,
  Keita Yoshioka, Olaf Kolditz}{11th European Solid Mechanics
  Conference}{04–08 July 2022}{Galway, Ireland}

\cventry{2022}{Investigating the high
  temperature visco-plastic behaviour of polycristalline
  \(UO_{2+x}\)}{Philippe Garcia, Jean-Baptiste Parise, Thomas Helfer,
  Audrey Miard, Marco Cologna, Guy Antoy and Xavière Iltis.}{Nuclear
  Materials Conference (NUMAT).}{24-28 October.}{Ghent, Belgium}

\cventry{2022}{Multiphysics modeling of
  adhesive interface with damage.}{Sébastien D’Andréa, Stéphane
  Lejeunes, Frédéric Lebon, Victor Blanc, Marc Lainet, Thomas
  Helfer.}{25ème Congrès Français de Mécanique}{}{}{}

\cventry{2022}{Development of a novel damage
  model for concrete accounting for creep, high temperature, and
  constraint effects.}{Jefri Draup, Alexandre Gangnant, Graham Doughty,
  Jiansong Guo, Thomas Helfer and Giacomo Torelli.}{SMiRT-26.}{
  Berlin/Potsdam, Germany.}{July 10-15, 2022}

\cventry{2022}{Analysing the compaction of
  crushed salt in repositories for high-level waste in salt formations
  using a dedicated constitutive model.}{Éric Simo, Thomas Nagel,
  Christian Lerch, Paola Léon Vargas and Thomas Helfer.}{EGU22
  meeting.}{Vienne.}{May 2022}

\cventry{2022}{Modélisation de l’amorçage et
  de la propagation de l’endommagement d’un milieu hétérogène de type
  matrice – inclusions soumis à des dilatations différentielles}{
  Vincent Gauthier, Mihail Garajeu, Bruno Michel, Thomas Helfer et
  Renaud Masson.}{25ème Congrès Français de Mécanique}{}{}

%\cventry{2022}{Premières démonstrations d’une
%  proto-application HPC en mécanique non linéaire implicit}{Guillaume
%  Latu et Thomas Helfer}{25ème Congrès Français de Mécanique}{}{}

\cventry{2022}{Simulation du comportement sous
  irradiation des gaines en alliage de zirconium.}{Cécilia Gicquel,
  Fabien Onimus, Renald Brenner, Thomas Helfer et Renaud Masson.}{25ème
  Congrès Français de Mécanique}{}{}

\cventry{2022}{Micromorphic damage behaviours
  for quasi-brittle materials: a numerical implementation and link with
  phase-field approach to fracture.}{David Siedel Olivier Fandeur,
  Thomas Helfer, Jacques Besson, Samuel Forest, Kaïs Ammar}{8th European
  Congress on Computational Methods in Applied Sciences and Engineering
  (ECCOMAS).}{Oslo.}{Norway}

\cventry{2022}{Polycrystalline simulations
  of in-reactor deformation of Zircaloy-4 cladding tubes during nominal
  operating conditions}{Cécilia Gicquel, Fabien Onimus, Renald Brenner,
  Thomas Helfer et Renaud Masson}{Zirconium in the Nuclear Industry}{}{}

\cventry{2022}{A gradient damage approach using
  the Hybrid High Order method}{David Siedel Olivier Fandeur, Thomas
  Helfer, Jacques Besson, Samuel Forest, Kaïs Ammar}{15th World Congress
  on Computational Mechanics (WCCM-XV) and 8th Asian Pacific Congress on
  Computational Mechanics (APCOM-VIII), Yokohama, Japan.}{}{}

\cventry{2022}{Data-Driven Simulations for Panel
  Paintings: modelling the experimental results.}{Lorenzo Riparbelli,
  Luca Uzielli, Paola Mazzanti, Ioannis Christovasilis, Thomas Helfer et
  Marco Fioravanti.}{15th World Congress on Computational Mechanics
  (WCCM-XV) and 8th Asian Pacific Congress on Computational Mechanics
  (APCOM-VIII), Yokohama, Japan.}{}{}

\cventry{2022}{Semi-supervised deep learning of
  constitutive relations.}{Marius Duvillard, Loïc Giraldi et Thomas
  Helfer.}{15th World Congress on Computational Mechanics (WCCM-XV) and
  8th Asian Pacific Congress on Computational Mechanics (APCOM-VIII),
  Yokohama, Japan.}{}{}

\cventry{2022}{Schéma de résolution locale pour la
  méthode Hybrid High Order et application en mécanique
  non-linéaire}{David Siedel, Thomas Helfer, Olivier Fandeur, Jacques
  Besson, Samuel Forest, Kaïs Ammar}{15ème Colloque National en Calcul
  des Structures, Giens, France.}{}{}

\cventry{2022}{Implicit integration of the
  constitutive equations of a polycrystal obtained by the
  Berveiller-Zaoui homogeneization scheme.}{Thomas Helfer, Cécilia
  Gicquel, Fabien Onimus et Renaud Masson.}{15ème Colloque National en
  Calcul des Structures, Giens, France.}{}{}

\cventry{2022}{New functionalities of Versions
  3.3, 3.4 and 4.0 of the TFEL/MFront project.}{Thomas Helfer, Jérémy
  Hure, Mohamed Shokeir, Olivier Fandeur, Olivier Jamond, Jean-Philippe
  Mathieu, Simon Raude, Dominique Geoffroy, Jérémy Bleyer, Thomas Nagel
  et Guillaume Latu.}{15ème Colloque National en Calcul des Structures,
  Giens, France.}{}{}

\cventry{2022}{MANTA : un code HPC généraliste pour
  la simulation de problèmes complexes en mécanique.}{Olivier Jamond,
  Nicolas Lelong, Axel Fourmont, Joffrey Bluthé, Matthieu Breuze, Pascal
  Bouda, Guillaume Brooking, Florence Drui, Alexandre Epalle, Olivier
  Fandeur, Gauthier Folzan, Thomas Helfer, Francis Kloss, Guillaume
  Latu, Antoine Motte, Christopher Nahed, Adrien Picard, Raphaël Prat,
  Isabelle Ramière, Morgane Steins et Benoît Prabel.}{15ème Colloque
  National en Calcul des Structures, Giens, France.}{}{}

\cventry{2021}{MFEM-MGIS-MFront, a
  MFEM-Based Library for Nonlinear Solid Thermomechanics}{Thomas Helfer
  et Guillaume Latu}{First MFEM
  workshope}{\url{https://www.youtube.com/watch?v=K6HrhFWdfx8&list=PLy9rIbGDXrG2vXwWJctvLAKz5xYjTRcR9&index=6}}{}{}

\cventry{2021}{Porous Crystal Plasticity-based
  Ductile Fracture assessment for FCC Nuclear materials.}{Cédri Sénac,
  Jérémy Hure, Jean-Michel Scherer, Thomas Helfer et Benoît
  Tanguy.}{European Nuclear Young Generation.}{}{}

\cventry{2021}{MFront: an open-source code
  generator for complex constitutive laws}{Thomas Helfer, Gentien
  Marois, Jérémy Bleyer}{14th World Congress on Computational
  Mechanics}{}{}

\cventry{2021}{mgis.fenics Part II: Cosserat
  media in small deformation with mgis.fenics.}{Tamara Dancheva, Unai
  Alonso, Michael Barton, Jérémy Bleyer, Thomas Helfer, Raffaele
  Russo.}{FEniCS
  2021.}{\url{https://www.researchgate.net/publication/350811403_mgisfenics_Part_II_Cosserat_media_in_small_deformation_with_mgisfenics}}{}

\cventry{2021}{mgis.fenics Part I: coupling
  MFront and FEniCS for complex solid mechanics simulations.}{Thomas
  Helfer, Jérémy Bleyer, Raffaele Russo, Tamara Dancheva.}{FEniCS
  2021}{\url{https://www.researchgate.net/publication/350819968_mgisfenics_Part_I_coupling_MFront_and_FEniCS_for_complex_solid_mechanics_simulations}}{}

\cventry{2020}{MGIS et mgis.fenics (The
  MFrontGenericInterfaceSupport project and its binding with
  FEniCS)}{Thomas Helfer et Jérémy Bleyer.}{Seminar on automatic
  code-generation tools organisé par le laboratoire Navier (École des
  Ponts)}{}{}

\cventry{2020}{MFront: code generator dedicated to
  material knowledge.} {Thomas Helfer et Jérémy Bleyer.}{Seminar on
  automatic code-generation tools organisé par le laboratoire Navier
  (École des
  Ponts)}{\url{https://www.youtube.com/watch?v=nldf7IEtnpM}}{}.

\cventry{2020}{Herausforderungen in der
  THMC Modellierung für die Endlagerforschung.}{Thomas Nagel, Lars
  Bilke, Jörge Buchwald, Aqeel Afzal Chaudhry, Uwe-Jens Görke, Norbert
  Grunwald, Thomas Helfer, Olaf Kolditz, Renchao Lu, Jobst Maßmann,
  Vanessa Montoya, Dmitri Naumov, Francesco Parisio, Haibing Shao, Hua
  Shao, Wenqing Wang, Keita Yoshioka.}{Tage der Standortauswahl,
  Braunschweig, Germany.}{}{}

\cventry{2019}{New functionalities of Versions 3.1 and 3.2 of
  TFEL/MFront}{Helfer, Thomas and Fandeur, Olivier and Geoffroy,
  Dominique and Toulemonde, Charles and Hure, Jérémy and Dupuy,
  Laurent and Forré, Agathe and Deloison, Dominique and Péralès,
  Frédéric and Lejeune, Arnaud and Thibault, Sébastien and Richard,
  Fabrice and Gaillard, Yves and Almanstötter, Jürgen and Gangnant,
  Alexandre and Draup, Jefry and Kececioglu, Anthony and Garnier,
  Christophe and Garnier, Christophe and Roland, Jérôme}{14ème
  Colloque National en Calcul des Structures, Giens, France}{}{}

\cventry{2019}{Development of a novel damage
  model for concrete subjected to high temperature and
  constraint.}{Proceeding of SMIRT 25. Charlotte,NC,USA, August
  2019.}{Jefry Draup, Alexandre Gangnant, Gaëtan Colette, Graham
  Doughty, Jiansong, Guo, Thomas Helfer, Giacomo Torelli et
  Parthasarathi
  Mandal}{\url{https://www.researchgate.net/publication/333783199_Development_of_a_Novel_Damage_Model_for_Concrete_Subjected_to_High_Temperature_and_Constraint}}{}

\cventry{2019}{High temperature creep study of
  recrystallized Tungsten: 3-point bending experiments and finite
  element simulation.}{Jean-Baptiste Parise, Philippe Garcia, Thomas
  Helfer, Audrey Miard, Alain Durif, Marianne Richou, Guy
  Antou.}{Plasma-Facing Materials and Components for Fusion Applications
  (PFMC)}{Eindhoven, Netherlands}{}

\cventry{2019}{Une implémentation numérique efficace
  pour le traitement de la fissuration fragile par champ de phase:
  application aux combustibles nucléaires}{Ye Lu, Thomas Helfer, Olivier
  Fandeur, Benoît Bary.}{Congrès Français de Mécanique}{}{}

\cventry{2019}{Comparison of different implicit
  integration procedures for an elasto-viscoplastic
  model.}{International Conference on Material Modelling (ICCM),
  Stockholm}{Agathe Forre, Thomas Helfer et Khouloud
  Derouiche}{\url{https://indico.lunarc.lu.se/event/1/contributions/125/}}{}

\cventry{2019}{MFrontInterface.jl:
  MFront material models in JuliaFEM.}{Tero Frondelius, Thomas Helfer,
  Ivan Yashchuk, Joona Vaara, Anssi Laukkanen.}{Proceedings of the 32
  nd Nordic Seminar on Computational Mechanics, Oulu , Finlande}{}{}

\cventry{2018}{High temperature creep of uranium
  dioxide: on the influence of equilibrium oxygen partial
  pressure.}{Philippe Garcia, Audrey Miard, Jean-Baptiste Parise, Mariem
  Ben Saada, Xavière Iltis, Clément Introni et Thomas Helfer.}{MRS
  spring meeting.}{Phoenix, USA.}{}

\cventry{2018}{Fast, Robust and Portable
  Implementations of Complex Mechanical Behaviours with the MFront Code
  Generator.}{Thomas Helfer}{13th World Congress on Computational
  Mechanics, New York, USA}{}{}

\cventry{2018}{A phase-field description of brittle
  crack propagation in nuclear fuels}{Thomas Helfer et Olivier
  Fandeur}{13th World Congress on Computational Mechanics, New York,
  USA}{}{}

\cventry{2017}{Modeling and simulation of
  cracking in quasi-fragile materials by using phase field method:
  Application to concrete.}{Tran Dang, Benoît Bary, Thomas Helfer,
  Qi-Chang He, Julien Yvonnet.}{ICF 2017 - 14th International Conference
  on Fracture.}{}{}

\cventry{2017}{Status of the DIAMINO experiment
  irradiated in the OSIRIS reactor.}{Syriac Bejaoui, Stéphane Bendotti,
  Thierry Lambert et Thomas Helfer.}{GLOBAL 2017 - International Nuclear
  Fuel Cycle Conference.}{Seoul, South Korea.}{}

\cventry{2017}{Modélisation par champ de
  phase de la fissuration des matériaux fragiles: Aspects numériques et
  applications au combustible nucléaire oxyde.}{Thomas Helfer, Benoît
  Bary, Tran Dang, Oliver Fandeur et Bruno Michel.}{13ème colloque
  national en calcul des structures. Giens, France}{}{}

\cventry{2017}{New functionalities of the 3.0 version
  of TFEL, MFront and MTest.}{Thomas Helfer, Olivier Fandeur, David
  Haboussa, Dominique Deloison, Olivier Jamond, Rémi Munier, Lucie
  Berthon, Étienne Castelier et Isabelle Ramière.}{13ème colloque
  national en calcul des structures. Giens, France}{}{}

\cventry{2017}{Insertion reliability studies for
  the RBC-type control rods in ASTRID}{Maxime Zabiégo, Denis Lorenzo,
  Thomas Helfer et Étienne Guillemin}{Proceedings of the FR17 IAEA
  Conference}{Yekaterinburg, Russian Federation}{}

\cventry{2016}{Implémentation de lois de
  comportement mécanique à l’aide du générateur de code MFront.}{Thomas
  Helfer.}{Séminaire IMSIA.}{Saclay, France}{}

\cventry{2016}{Using Anderson Algorithm to accelerate FFT Based
  methods.}{Étienne Castelier, Lionel Gélébart
  et Thomas Helfer.}{ECCOMAS}{}{}

\cventry{2015}{Numerical Analysis of Concrete
  Creep on Mesoscopic 3D Specimens.}{Benoît Bary, Christophe Bourcier et
  Thomas Helfer.}{Proceedings of the 10th International Conference on
  Mechanics and Physics of Creep, Shrinkage, and Durability of Concrete
  and Concrete Structures.}{}{}

\cventry{2015}{Advanced mechanical resolution in
  CYRANO3 fuel performance code using MFront generation tool.}{Charles
  Petry et Thomas Helfer.}{LWR Fuel Performance Meeting/TopFuel/WRFPM.
  Zurich, Switzerland}{}{}

\cventry{2015}{2D simulations of hydride blister
  cracking during a RIA transient with the fuel code ALCYONE.}{Jérôme
  Sercombe, David le Boulch, Thomas Le Jolu, Arthur Hellouin de Menibus,
  Thomas Helfer, Éric Fédérici, et Christian Bernaudat.}{LWR Fuel
  Performance Meeting/TopFuel/WRFPM. Zurich,
  Switzerland.}{\url{https://hal.archives-ouvertes.fr/cea-02500835}}{}

\cventry{2015}{Characterization,
  Simulation and Improvement of Spacer Pads Mechanical Behaviour for
  Sodium Fast Reactor Fuel Subassemblies}{Victor Blanc, Xavier
  Jeanningros, Thomas Helfer, Pierre Lamagnère, et Thierry Beck}{SMIRT
  23 - 23th International Conference on Structural Mechanics in Reactor
  Technology}{\url{https://hal.archives-ouvertes.fr/cea-02492561/}}{}

\cventry{2015}{Recent improvements of the fuel
  thermomechanical modelling in the PLEIADES Platform to better simulate
  accidental transients conditions using the Alcyone fuel performance
  code.}{Thomas Helfer, Jérôme Sercombe, Bruno Michel, Isabelle Ramière,
  Maxime Salvo, Olivier Fandeur, Patrick Goldbronn, Vincent Marelle,
  Éric Fédérici.}{NuFuel \& MMSNF 2015, Karlsruhe, Germany.}{}{}

\cventry{2015}{Implantation de lois de
  comportement mécanique à l’aide de MFront : Simplicité, efficacité,
  robustesse et portabilité.}{Thomas Helfer, Jean-Michel Proix, Olivier
  Fandeur.}{12ème colloque national en calcul des structures. Giens,
  France}{}{}

\cventry{2013}{Recent modelling improvements in
  fuel performance code {GERMINAL} for {SFR} oxide fuel pins}{Marc
  Lainet, Vincent Bouineau, Thomas Helfer, Pelletier Michel}{Proceedings
  of the International Conference on Fast Reactors and Related Fuel
  Cycles: Safe Technologies and Sustainable Scenarios, Paris}{}{}

\cventry{2013}{Thermomechanical
  simulation of the Diamino irradiation experiment using the LICOS fuel
  design code.}{Syriac Bejaoui, Thomas Helfer, Éric Brunon, Thierry
  Lambert, Cédric Neyroud, Stephane Bendotti}{Global 2013, Salt Lake
  City, UT}{}{}

\cventry{2013}{State of the art of the conceptual
  designs for ASTRID control and shutdown rods.}{Isabelle
  Guénot-Delahaye, Denis Lorenzo, Bernard Valentin, Jean-Michel Escleine
  et Thomas Helfer.}{Proceedings of the International Conference on Fast
  Reactors and Related Fuel Cycles: Safe Technologies and Sustainable
  Scenarios}{}{}

\cventry{2009}{The fuel performance code Celaeno,
  conception and simulation of fuel elements for gas-cooled fast
  reactor.}{Thomas Helfer, Éric Brunon, Étienne Castelier, Alain Ravenet
  et Nathalie Chauvin.}{Proceedings of GLOBAL 2009 conference on
  advanced nuclear fuel}{}{}

\cventry{2005}{Modelling the effect of oxide
  fuel fracturing on the mechanical behaviour of fuels rods}{Thomas
  Helfer, Philippe Garcia, Jean-Marc Ricaud, David Plancq, Christine
  Struzik, François Sidoroff et L. Bernard}{Pellet-clad Interaction in
  Water Reactor Fuels: Seminar Proceedings}{Aix en Provence, France}{}

\cventry{2004}{PLEIADES : a unified environment
  for multi-dimensional fuel performance modeling.}{David Plancq, Gilles
  Thouvenin, Jean-Marc Ricaud, Christine Struzik, Thomas Helfer, Fabrice
  Bentejac, Philippe Thévenin et Renaud Masson.}{International meeting
  on LWR fuel performance, Floride.}{}{}

\section{Rapport techniques publiques}

\cventry{2020}{Assisted computation of the
  consistent tangent operator of behaviours integrated using an implicit
  scheme. Theory and implementation in MFront.}{Thomas Helfer.}{Documentation du projet MFront.}{\url{https://www.researchgate.net/publication/342721072_Assisted_computation_of_the_consistent_tangent_operator_of_behaviours_integrated_using_an_implicit_scheme_Theory_and_implementation_in_MFront}}{}

\cventry{2020}{Small-strain von mises
  elastoplasticity.}{Jérémy Bleyer et Thomas Helfer.}{Documentation du
  projet
  mgis.fenics.}{\url{https://www.researchgate.net/publication/340953012_Small-strain_von_Mises_elastoplasticity}}{}

\cventry{2020}{Jérémy Bleyer et Thomas
  Helfer}{Transient heat equation with phase change}{Documentation du
  projet
  mgis.fenics}{\url{https://www.researchgate.net/publication/341359549_Transient_heat_equation_with_phase_change}}{}

\cventry{2020}{Monolithic transient
  thermo-elasticity.}{Jérémy Bleyer et Thomas Helfer.}{Documentation du
  projet
  mgis.fenics.}{\url{https://www.researchgate.net/publication/341372231_Monolithic_transient_thermo-elasticity}}{}

\cventry{2020}{Stationnary non-linear heat
  transfer using mgis.fenics.}{Jérémy Bleyer et Thomas
  Helfer.}{Documentation du projet
  mgis.fenics.}{\url{https://www.researchgate.net/publication/340965420_Stationnary_non-linear_heat_transfer_using_mgisfenics}}{}


\cventry{2020}{Stationnary non-linear heat
  transfer: 3D problem and performance comparisons.}{Jérémy Bleyer et
  Thomas Helfer.}{Documentation du projet
  mgis.fenics.}{\url{https://thelfer.github.io/mgis/web/mgis_fenics_nonlinear_heat_transfer_3D.html}}{}


\cventry{2020}{Phase-field approach to brittle
  fracture.}{Jérémy Bleyer et Thomas Helfer.}{Documentation du projet
  mgis.fenics}{\url{https://www.researchgate.net/publication/341359638_Phase-field_approach_to_brittle_fracture}}{}

\cventry{2020}{Overview of the mgis.fenics
  module.}{Jérémy Bleyer et Thomas Helfer.}{Documentation du projet
  mgis.fenics.}{\url{https://www.researchgate.net/publication/340952899_Overview_of_the_mgisfenics_module}}{}

\cventry{2020}{Finite-strain
  elastoplasticity within the logarithmic strain framework.}{Jérémy
  Bleyer et Thomas Helfer}{Documentation du projet
  mgis.fenics.}{\url{https://www.researchgate.net/publication/340953042_Finite-strain_elastoplasticity_within_the_logarithmic_strain_framework}}{}


\cventry{2020}{Extending the
  StandardElastoViscoPlasticity brick with a new stress
  criterion.}{Thomas Helfer, Jérémy Hure, Mohamed Shokeir}{Documentation
  du projet
  MFront}{\url{https://www.researchgate.net/publication/340280305_Extending_the_StandardElastoViscoPlasticity_brick_with_a_new_stress_criterion}}{}

\cventry{2020}{Using MFront as a wrapper for a
  thermo-hydro-mechanical behaviour for bentonite available in the TRIAX
  package.}{Thomas Helfer, Thomas Nagel et David Mašín.}{Documentation
  du projet
  MFront}{\url{https://www.researchgate.net/publication/342747050_Using_MFront_as_a_wrapper_for_a_thermo-hydro-mechanical_behaviour_for_bentonite_available_in_the_TRIAX_package}}{}

\cventry{2020}{A brief introduction
  to the MGIS C++ library for mechanical behaviours.}{Documentation du
  projet
  mgis}{Thomas Helfer}{\url{https://www.researchgate.net/publication/333089236_A_brief_introduction_to_the_MGIS_C_library_for_mechanical_behaviours}}{}

\cventry{2019}{Elasto-plastic analysis
  implemented using the MFront code generator.}{Jérémy Bleyer et Thomas
  Helfer}{Numerical tours of continuum mechanics using
  FEniCS}{\url{Available from:
    https://comet-fenics.readthedocs.io/en/latest/demo/plasticity_mfront/plasticity_mfront.py.html}}{}

\cventry{2017}{How to implement an isotropic
  viscoplastic behaviour combining isotropic hardening and multiple
  kinematic hardenings following an Armstrong-Frederic evolution of the
  back stress.}{Thomas Helfer.}{Documentation of the MFront
  project}{\url{https://thelfer.github.io/tfel/web/isotropicplasticityamstrongfrederickinematichardening.html}}{}

\section{Sites web}

\cventry{}{The \texttt{TFEL/MFront} project}{\url{https://thelfer.github.io/tfel/web/index.html}}{}{}{}{}
\cventry{}{The \texttt{MGIS} project}{\url{https://thelfer.github.io/mgis/web/index.html}}{}{}{}{}
\cventry{}{The \texttt{MFrontGallery} project}{\url{https://thelfer.github.io/MFrontGallery/web/index.html}}{}{}{}{}
\cventry{}{The \texttt{MFEM/MGIS} project}{\url{https://thelfer.github.io/mfem-mgis/web/index.html}}{}{}{}{}
